Evidence accumulation modelling offers new insights into the cognitive mechanisms that underlie linguistic and action-based training

### 2024-11-29 manuscript/manuscript.Rmd
added the updated figures to the manuscript

```{r accuracy-rt-plot, fig.cap = "(ref:accuracy-rt-caption)"}
knitr::include_graphics("../figures/from_file/acc_rt.png")
```

@@

```{r threshold-plot, fig.cap = "(ref:threshold-caption)"}
knitr::include_graphics("../figures/from_file/thresholds.png")
```

@@

```{r drift-rate-plot, fig.cap = "(ref:drift-rate-caption)"}
knitr::include_graphics("../figures/from_file/drift_rate.png")
```

@@

```{r ndt-plot, fig.cap = "(ref:ndt-caption)"}
knitr::include_graphics("../figures/from_file/ndt.png")
```

@@

```{r lba-summary-plot, fig.cap = "(ref:lba-summary-caption)"}
knitr::include_graphics("../figures/lba_summary.jpeg")
```

>>>>

```{r accuracy-rt-plot, fig.cap = "(ref:accuracy-rt-caption)"}
knitr::include_graphics("../figures/descriptive/violin_acc_rt.jpeg")
```

@@

```{r threshold-plot, fig.cap = "(ref:threshold-caption)"}
knitr::include_graphics("../figures/ea/thresholds.jpeg")
```

@@

```{r drift-rate-plot, fig.cap = "(ref:drift-rate-caption)"}
knitr::include_graphics("../figures/ea/drift_rate.jpeg")
```

@@

```{r ndt-plot, fig.cap = "(ref:ndt-caption)"}
knitr::include_graphics("../figures/ea/ndt.jpeg")
```

@@

```{r lba-summary-plot, fig.cap = "(ref:lba-summary-caption)"}
knitr::include_graphics("../figures/ea/lba_summary.jpeg")
```

### 2024-11-29 manuscript/manuscript.tex
added the updated figures to the manuscript

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\makeatother
\keywords{evidence accumulation modelling, training, learning, action, naming, cognitive mechanisms, plasticity\newline\indent Word count: 6679}
\usepackage{lineno}

@@

{\centering \includegraphics[height=0.67\textheight,]{../figures/from_file/acc_rt}

@@

{\centering \includegraphics[height=0.67\textheight,]{../figures/from_file/thresholds}

@@

{\centering \includegraphics[height=0.67\textheight,]{../figures/from_file/drift_rate}

@@

{\centering \includegraphics[height=0.67\textheight,]{../figures/from_file/ndt}

@@

{\centering \includegraphics[height=0.67\textheight,]{../figures/lba_summary}

>>>>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\makeatother
\keywords{evidence accumulation modelling, training, learning, action, naming, cognitive mechanisms, plasticity\newline\indent Word count: 6703}
\usepackage{lineno}

@@

{\centering \includegraphics[height=0.67\textheight,]{../figures/descriptive/violin_acc_rt}

@@

{\centering \includegraphics[height=0.67\textheight,]{../figures/ea/thresholds}

@@

{\centering \includegraphics[height=0.67\textheight,]{../figures/ea/drift_rate}

@@

{\centering \includegraphics[height=0.67\textheight,]{../figures/ea/ndt}

@@

{\centering \includegraphics[height=0.67\textheight,]{../figures/ea/lba_summary}
